Estimating duration in the presence of misclassification

### 2024-01-25 transmission.tex
Compare model outputs

\section{Conclusion}

>>>>

\begin{figure}
    \centering \includegraphics{transmission/compare-regions}
    \caption[Comparing each models estimate of regional incidence.]{%
        Incidence proportion in England and each region estimated by the two models discussed in this chapter.
        Posterior median and 95\% CrI shown.
        For the SEIR model, newly PCR positive (entrances into the P1 compartment), rather than incidence (entrances into the E compartment) are shown for comparability with the backcalculation results.
    }
    \label{transmission:fig:compare-regions}
\end{figure}

\begin{figure}
    \centering \includegraphics{transmission/compare-NE}
    \caption[Comparing each models estimate of North East incidence by age.]{%
        Incidence proportion in each age group in the North East estimated by the two models discussed in this chapter.
        Posterior median and 95\% CrI shown.
        For the SEIR model, newly PCR positive (entrances into the P1 compartment), rather than incidence (entrances into the E compartment) are shown for comparability with the backcalculation results.
    }
    \label{transmission:fig:compare-NE}
\end{figure}
\section{Conclusion}
